### 2024-10-04 texts/paper_closing.tex
minor rewriting/relabellign, move museum regulation to measurement

% Created 2024-10-03 do 13:26
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

\subsubsection*{definition}

@@

Existing research on private museum is conducted primarily by scholars of the art field or market as well as art historians.
Nethertheless, the identification of the centrality of the founder as a critical source of vulnerability corresponds strongly to the finding in non-profit management of a relation between diversification and mortality \parencite{Tuckman_Chang_1991_vulnerability}.
For example, \textcite{Bielefeld_1994_survival} finds that nonprofits with a larger number of funding sources (e.g. from foundations, individuals, federated funders, corporations, trusts, government at federal, state, county and municipal level as well as self-generated sources such as dues, interests, and service revenue, p.31) are more likely to survive.
Other studies have measured diversification as the Herfindahl Index (a measure of concentration) of income sources such as public support, program service revenues, dues and assessments, net fundraising income and profits from sale of inventory \parencite[p.381]{Hager_2001_vulnerability} or contributions, program service revenue, investment income, other revenues \parencite[p.37]{Lu_Shon_Zhang_2019_dissolution}, with both studies finding a positive association between diversification and survival; in the case of \textcite{Hager_2001_vulnerability} also specifically for art museums.
Next to diversification, volatility, i.e. fluctuation in revenue streams, has been associated with mortality as well \parencite{Mayer_2022_simmer}.
Despite limited reception of this research stream in the private museum literature, identifying the high reliance on the founder as a source of risk thus corresponds to management insights. 
Resulting from the dependence of the museum on the founder, it is plausible that interruptions to this key revenue source would endanger the viability of the museum, which can be formulated as: 
\bigbreak
\noindent
\textbf{Hypothesis 1}: Events which disrupt the founder's ability to provide resources to their private museums increase the risk of closing.

@@

While limited research exists that investigates reputation effects for (art) museums, its effects have been investigated for non-profits more widely.
Here reputation is often referred to as an organization's resource or asset \parencite{Kong_Farrell_2010_image,Goldfarb_Zavyalova_Pillai_2018_Rao,Walker_McCarthy_2010_survival,Schloderer_Sarstedt_Ringle_2014_reputation}. 
Studies primarily focus on the effect of reputation on some tangible benefits such as donations and contributions \parencite{Sarstedt_2010_reputation,Mews_Boenigk_2012_blood,Heller_2008_alliances,Meijer_2009_reputation}, or its direct effect on survial \parencite{Lu_Shon_Zhang_2019_dissolution,Singh_1991_change,Hager_2001_vulnerability,Bielefeld_1994_survival,HernandezOrtiz_2022_discontinuity}\footnote{Furthermore, the term "survival" is sometimes used more loosely to refer to a non-profit's effective operation and financial condition rather than the more narrowly defined dissolution (e.g. \cite[p.58]{Santos_Laureano_Moro_2019_reputation}, \cite[p.15]{Heller_2008_alliances}, \cite[p.111]{Schloderer_Sarstedt_Ringle_2014_reputation})}, with most studies finding support for a positive effect of reputation.
Next to the reputation of the general public, studies have also found reputation effects among more narrowly defined groups, in particular peers \parencite{Padanyi_Gainer_2003_peerreputation} and networks of similar organizations on regional and national scale \parencite{Walker_McCarthy_2010_survival}.
In particular this reputation among more narrowly defined groups makes it likely that the reputation of the  \emph{founder} matters (beyond the reputation of the \emph{organization}, the focus on most prior research) given the highly personal character of the private museum initiative and the central role of the founder in negotiations with decision makers from other organizations or the public sector.

In the case of the founder losing his reputation, the consequences then might extend beyond personal demotivation.
Such a decline could also curtail potential opportunities for cooperation with other institutions and limit the museum's reach to larger audiences, thus posing a risk to the museum's continued operation and survival in the long term.
\bigbreak
\noindent
\textbf{Hypothesis 1b}: Private museums are more likely to close after a decline of their founder's status.

@@

The perception of the museum itself, beyond the reputation of the founder, might also affect survival prospects.
An identity that is legitimate (understandable) and favorable (positive) has been argued to have a vast number of positive outcomes for organizations such as allowing higher profits, satisfaction, as well as weaker impact of shocks, and providing the opportunity to deviate from established patterns  \parencite{Lange_Lee_Dai_2010_reputation}, which in turn can facilitate survival prospects \parencite{Rao_1994_reputation}.
In the context of private museums, a more positive identity could lead to higher visitor numbers, discounts from art dealers, government grants or collaborations with other museums or corporations, resulting in higher revenues and lower acquisition costs.

Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
Next to material organizational features, adherence to naming conventions has been found to enhance legitimacy \parencite{Glynn_Abzug_2002_names}; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate. 
However, the category of museums could be relatively flexible (for example, the term "museum" is generally not subject to state regulation in the US or Germany \parencite{Museumsbund_ICOMDE_2006_standards,Lister_2023_marketing}), which might result in a relatively high tolerance of diversity and hence limited devaluation of non-conforming, atypical members \parencite{Bogaert_etal_2014_ecological}.

\bigbreak
\noindent
\textbf{Hypothesis 4}: Private museums with more understandable identities, indicated by adherence to naming conventions, are less likely to close.

It is however necessary to consider that in particular the name of a museum might be associated with a museum's survival via identity, but also reflect founder intentions regarding the institutions longevity; this possibility is discussed in more detail in the results section.
\paragraph*{Competition}

@@

In particular, Cox proportional hazard models allows to identify the risk that a number of variables pose for a museum's chance of closing. 
The dependent variable is an indicator of museum closure, which takes the value of 1 for the museums which close in the year of their closure, and 0 otherwise.
Typically for survival data, museums that do not close during the observation period are right-censored, i.e. for such museums the dependent variable is zero for all years as their closing has not been observed.
The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), where \(\psi = \exp(\sum_{j} \mathbf{x}_j \beta_j)\); with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient vector.
Partial maximum likelihood estimation allows calculating \(\beta\) without defining the baseline hazard rate, which therefore is not constrained to a parametric form \parencite{Moore_2015_survival}.
\subsubsection*{Main Predictors (Cox Proportional Hazards Model)}

@@

A measure of founder death is constructed as a time-varying covariate, which takes the value of 1 from the year of the founder's death onwards.
\paragraph*{Legitimacy}

@@

Two measures are constructed that aim to capture an effect of legitimacy on closing.
First, self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent, see table \ref{tbl:t_selfid}).
Since the name is one of the first aspects that stakeholders perceive when engaging with an organization, it might shape expectations and influence forms of engagement.
In particular, it might be that museums that also refer to themselves as museums are seen as more favorable and worthy of visits, collaborations and support than other museums.

To ensure that inclusion of the word "museum" corresponds to the naming convention of the museum population, the names of the "Museums of the World" (MOW) database \parencite{deGruyter_2021_MOW}, a database containing over 55,000 museums, are analyzed.
In this database, 71\% of museum names contain the term "museum" (or its equivalent in other languages), which indicates a substantial convention by founders to include the term museum in the name of their institution.\footnote{While it would also be possible to construct inclusion in the MOW as an indicator of legitimacy, as it represents recognition of the organization as a museum by experts \parencite{Zuckerman_1999_illegitimacy}, preliminary investigations of the database indicated that it has been  updated only sparsely in recent years; thereby inclusion in it (or the lack therefore) does not constitute an accurate measurement of the extent of an institutions' recognition as a museum.}
\paragraph*{Reputation}

Reputation is measured via inclusion of the founder in the Artnews top 200 collector ranking \parencite{Artnews_ranking}.
This ranking, established in 1990, lists each year the 200 collectors the editors of the magazine consider most relevant.
For each year, a museums can have one of three values: "Not included"; in which case the founder is not included in the year in question and has not been so in the past, "Included"; when the founder is included, or "Dropped", for cases where the founder was included at some point in the past but is no longer included in the current year.
Cases where multiple individuals are involved in the founding of a private museum are resolved by aggregating the Artnews ranking inclusion history to the founder level (i.e., if only one of two founders is dropped from the Artnews ranking but the other remains included, the founder couple as a whole is considered included).
The variable is lagged by one year to avoid reverse causality, i.e. to exclude the possibility that an association is observed which is present due to founders being dropped from the ranking as a consequence of the closure of their museum.
\paragraph*{Competition}

On a national level, density of private museum is calculated as the number of private museums per million population.
To measure competition on a local level, I first determine the coordinates of museum using the Google Maps API; the coordindates of museums which are not found that way (particularly those located in countries with limited Google presence such as South Korea, China and Russia) are searched manually (often using other map services such as Kakao Maps, Baidu Maps and Yandex Maps).
For closed museums, which often are not included in the current map databases, coordinates are also determined via addresses mentioned on snapshots in the Wayback Machine.
I then use the Global Human Settlement Layer \parencite{EC_2023_GHSL} to estimate the number of private museums and population counts inside a radius of ten kilometers around each private museum for each year.
To be able to estimate both competition and demand/audience/population separately, I do not calculate densities as per capita rates, but include the local museum counts, local population in millions as well as an interaction between the two.
\subsubsection*{Control variables}

@@

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep 27 17:51:17 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 294 & 0.584 &  6.0e-01 &  0.489 & 0 & 1 \\ 
   & Gender - Female & 79 & 0.157 &  1.7e-01 &  0.372 & 0 & 1 \\ 
   & Gender - Couple & 130 & 0.258 &  2.3e-01 &  0.421 & 0 & 1 \\ 
   & Founder - alive &  &  &  9.0e-01 &  0.296 & 0 & 1 \\ 
   & Founder - died recently &  &  &  1.3e-02 &  0.115 & 0 & 1 \\ 
   & Founder - died 2+ years ago &  &  &  8.4e-02 &  0.277 & 0 & 1 \\ 
   & Founder died &  &  &  9.7e-02 &  0.296 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 190 & 0.378 &  4.1e-01 &  0.491 & 0 & 1 \\ 
   & Self-Identification - Foundation & 104 & 0.207 &  1.9e-01 &  0.391 & 0 & 1 \\ 
   & Self-Identification - Collection & 69 & 0.137 &  1.3e-01 &  0.336 & 0 & 1 \\ 
   & Self-Identification - Other & 140 & 0.278 &  2.7e-01 &  0.446 & 0 & 1 \\ 
   & Founder name in Museum name & 240 & 0.477 &  4.8e-01 &  0.500 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  &  8.0e-01 &  0.398 & 0 & 1 \\ 
   & AN Ranking - Included &  &  &  1.4e-01 &  0.351 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  &  5.3e-02 &  0.225 & 0 & 1 \\ 
   & Exhibition any &  &  &  6.3e-01 &  0.483 & 0 & 1 \\ 
   & Opening year &  &  &  2.0e+03 & 11.104 & 1960 & 2020 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  &  4.5e-01 &  1.261 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  &  1.3e+00 &  1.682 & 0.000087 & 10.81 \\ 
   & Nbr PM within 10km &  &  &  1.8e+00 &  3.143 & 0 & 16 \\ 
   & PM density (10km, log) &  &  &  5.3e-01 &  0.786 & 0 & 4.35 \\ 
   & Nbr PM within 10km (log) &  &  &  6.1e-01 &  0.816 & 0 & 2.83 \\ 
   & Pop. (millions) within 10km (log) &  &  & -8.9e-01 &  1.966 & -9.3 & 2.38 \\ 
   & Local Audience per PM &  &  &  5.7e-01 &  0.865 & 0.000087 & 8.16 \\ 
   & Local Audience per PM (log) &  &  & -1.5e+00 &  1.638 & -9.3 & 2.10 \\ 
   & Region - Africa & 8 & 0.016 &  1.2e-02 &  0.110 & 0 & 1 \\ 
   & Region - Asia & 142 & 0.282 &  2.9e-01 &  0.455 & 0 & 1 \\ 
   & Region - Europe & 248 & 0.493 &  5.0e-01 &  0.500 & 0 & 1 \\ 
   & Region - Latin America & 23 & 0.046 &  4.2e-02 &  0.201 & 0 & 1 \\ 
   & Region - North America & 72 & 0.143 &  1.4e-01 &  0.345 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.020 &  1.9e-02 &  0.135 & 0 & 1 \\ 
   & UN Subregion - Northern Africa & 1 & 0.002 &  8.2e-04 &  0.029 & 0 & 1 \\ 
   & UN Subregion - Northern America & 72 & 0.143 &  1.4e-01 &  0.345 & 0 & 1 \\ 
   & UN Subregion - Eastern Asia & 96 & 0.191 &  2.2e-01 &  0.411 & 0 & 1 \\ 
   & UN Subregion - Southern Asia & 9 & 0.018 &  1.5e-02 &  0.120 & 0 & 1 \\ 
   & UN Subregion - South-eastern Asia & 12 & 0.024 &  2.5e-02 &  0.155 & 0 & 1 \\ 
   & UN Subregion - Southern Europe & 70 & 0.139 &  1.5e-01 &  0.361 & 0 & 1 \\ 
   & UN Subregion - Australia and New Zealand & 10 & 0.020 &  1.9e-02 &  0.135 & 0 & 1 \\ 
   & UN Subregion - Western Asia & 25 & 0.050 &  3.7e-02 &  0.189 & 0 & 1 \\ 
   & UN Subregion - Eastern Europe & 22 & 0.044 &  5.0e-02 &  0.218 & 0 & 1 \\ 
   & UN Subregion - Northern Europe & 27 & 0.054 &  5.7e-02 &  0.231 & 0 & 1 \\ 
   & UN Subregion - Western Europe & 129 & 0.256 &  2.4e-01 &  0.425 & 0 & 1 \\ 
   & UN Subregion - Sub-Saharan Africa & 7 & 0.014 &  1.1e-02 &  0.107 & 0 & 1 \\ 
   & UN Subregion - Latin America and the Caribbean & 23 & 0.046 &  4.2e-02 &  0.201 & 0 & 1 \\ 
   & Time Period 2000-2004 &  &  &  1.0e-01 &  0.301 & 0 & 1 \\ 
   & Time Period 2005-2009 &  &  &  1.7e-01 &  0.372 & 0 & 1 \\ 
   & Time Period 2010-2014 &  &  &  2.6e-01 &  0.438 & 0 & 1 \\ 
   & Time Period 2015-2019 &  &  &  3.3e-01 &  0.471 & 0 & 1 \\ 
   & Time Period 2020-2024 &  &  &  1.4e-01 &  0.352 & 0 & 1 \\ 
   & Great Recession (2008/09) &  &  &  7.6e-02 &  0.265 & 0 & 1 \\ 
   & Covid Pandemic (2020/21) &  &  &  1.4e-01 &  0.352 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

Before discussing the regression models, I provide a descriptive account on private museum closure using the hazard and survival functions which describe variation the closing risk over the museum life-course.
The hazard rate is a non-parametric function which describes the probability of exiting at age \(t_i\) (conditional on being alive), in the context of museum-years as units of analysis it can be formulated as \(h(t_i) = \frac{d_i}{n_i}\), with \(n_i\) as the number of units at risk at age \(t_i\) and \(d_i\) as the number of exits at age \(t_i\).
The survival function is the product of these conditional probabilities (\(S(t) = \prod_{t_i \geq t} \left(1-h(t_i) \right)\)) and describes the chance of surviving up to age \(t_i\).

@@

Calculating such survival statistics allows (to a degree) to assess whether private museums differ in their longevity from comparable institutions.
So far only a small number of studies has investigated museum closing rates, and these have focused on the United States, likely primarily due to data availability reasons: 
Larger non-profits in the US have to file the IRS form 990 (or its variants) to maintain their tax-deductible status, and form data is publicly available \parencite{Lecy_2023_core,Lecy_2023_core}.
This data has been used in many studies of non-profit populations, and constitutes an effective comparison group for private museums as both share the same organizational form (non-profit) and unprofitable cultural sector environment.
So far three studies have used this data to investigate museum closure by calculating hazard rates not as a function of age age but of calendar year:
\begin{itemize}
\item \textcite{Bowen_etal_1994_charitable} investigate the closing of 501(c)(3) museums in the 1981-1991 time period and, based on 271 (9.8\%) closures of a population of 2755, calculate average annual exit rates as 1.1\% (p.103).
\item \textcite{Gordon_etal_2013_insolvency} observe 35 closures over the years of 2000-2003 with 5,167 museum-years (p.368), resulting in an average annual closing rate of 0.68\% (p.377).
\item \textcite{Hager_2001_vulnerability} has conducted the only study specifically on art museums (NTEE code A51); he observes 42 closures over a period of four years (1994-1997) from a starting populaton of 448 (p.383), corresponding to an average yearly closing rate of 2.4\%, or around 1.9\% under the more realistic assumption of effectively using a five-year time period.
\end{itemize}

@@

The death of the founder is not associated with a significant difference (p=0.52) in private museum closure, i.e. museums are not significantly more likely to close after their founder has died, which provides little support to H2a.
While the point estimate is positive (0.280, corresponding to a  32\% increase in mortality for museums whose founders have died compared to those who have not), the low risk overall means that despite the cumulative character even decade-long survival times do not differ substantially (figure \ref{fig:p_surv_death}).

>>>>

% Created 2024-10-04 vr 15:42
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

@@

Existing research on private museum is conducted primarily by scholars of the art field or market as well as art historians.
Nethertheless, the identification of the centrality of the founder as a critical source of vulnerability corresponds strongly to the finding in non-profit management of a relation between diversification and mortality \parencite{Tuckman_Chang_1991_vulnerability,Hung_Hager_2018_diversification}.
For example, \textcite{Bielefeld_1994_survival} finds that nonprofits with a larger number of funding sources (e.g. from foundations, individuals, federated funders, corporations, trusts, government at federal, state, county and municipal level as well as self-generated sources such as dues, interests, and service revenue, p.31) are more likely to survive.
Other studies have measured diversification as the Herfindahl Index (a measure of concentration) of income sources such as public support, program service revenues, dues and assessments, net fundraising income and profits from sale of inventory \parencite[p.381]{Hager_2001_vulnerability} or contributions, program service revenue, investment income, other revenues \parencite[p.37]{Lu_Shon_Zhang_2019_dissolution}, with both studies finding a positive association between diversification and survival; in the case of \textcite{Hager_2001_vulnerability} also specifically for art museums.
Next to diversification, volatility, i.e. fluctuation in revenue streams, has been associated with mortality as well \parencite{Mayer_2022_simmer}.
Despite limited reception of this research stream in the private museum literature, identifying the high reliance on the founder as a source of risk thus corresponds to management insights. 
Resulting from the dependence of the museum on the founder, it is plausible that interruptions to this key revenue source would endanger the viability of the museum, which can be formulated as: 
\bigbreak
\noindent
\textbf{Hypothesis 1}: Events which disrupt the founder's ability to provide resources to their private museums increase the risk of closing.

@@

While limited research exists that investigates reputation effects for (art) museums, its effects have been investigated for non-profits more widely.
Here reputation is often referred to as an organization's resource or asset \parencite{Kong_Farrell_2010_image,Walker_McCarthy_2010_survival,Schloderer_Sarstedt_Ringle_2014_reputation}. 
Studies primarily focus on the effect of reputation on some tangible benefits such as donations and contributions \parencite{Sarstedt_2010_reputation,Mews_Boenigk_2012_blood,Heller_2008_alliances,Meijer_2009_reputation}, or its direct effect on survial \parencite{Lu_Shon_Zhang_2019_dissolution,Singh_1991_change,Hager_2001_vulnerability,Bielefeld_1994_survival,HernandezOrtiz_2022_discontinuity}\footnote{Furthermore, the term "survival" is sometimes used more loosely to refer to a non-profit's effective operation and financial health rather than the more narrowly defined dissolution (e.g. \cite[p.58]{Santos_Laureano_Moro_2019_reputation}, \cite[p.15]{Heller_2008_alliances}, \cite[p.111]{Schloderer_Sarstedt_Ringle_2014_reputation})}, with most studies finding support for a positive effect of reputation.
Next to the reputation of the general public, studies have also found reputation effects among more narrowly defined groups, in particular peers \parencite{Padanyi_Gainer_2003_peerreputation} and networks of similar organizations on regional and national scale \parencite{Walker_McCarthy_2010_survival}.
In particular this reputation among more narrowly defined groups makes it likely that the reputation of the  \emph{founder} matters (beyond the reputation of the \emph{organization}, the focus on most prior research) given the highly personal character of the private museum initiative and the central role of the founder in negotiations with decision makers from other organizations or the public sector.

In the case of the founder losing their reputation, the consequences then might extend beyond personal demotivation.
Such a decline could also curtail potential opportunities for cooperation with other institutions and limit the museum's reach to larger audiences, thus posing a risk to the museum's continued operation and survival in the long term.
\bigbreak
\noindent
\textbf{Hypothesis 1b}: Private museums are more likely to close after a decline of their founder's status.

@@

The perception of the museum itself, beyond the reputation of the founder, might also affect survival prospects.
As has also been summarized in the previous section, an identity that is legitimate (understandable) and favorable (positive) has been argued to have a large number of positive outcomes for organizations such as allowing higher profits, satisfaction, as well as weaker impact of shocks, and providing the opportunity to deviate from established patterns \parencite{Lange_Lee_Dai_2010_reputation}, which in turn can facilitate survival prospects \parencite{Rao_1994_reputation}.
In the context of private museums, a more positive identity could lead to higher visitor numbers, discounts from art dealers, government grants or collaborations with other museums or corporations, resulting in higher revenues and lower acquisition costs.

A favorable identity might be obtained by isomorphism, i.e. adopting features from established organizational  blueprints \parencite{diMaggio_1983_iron}.
Next to material organizational features, adherence to symbolic features such as naming conventions has been found to enhance perceptions of legitimacy; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate \parencite{Glynn_Abzug_2002_names}.
Assuming that such a legitimacy effect translates into better survival prospect, a hypothesis can be formulated as:

\bigbreak
\noindent
\textbf{Hypothesis 2}: Private museums with more understandable identities, indicated by adherence to naming conventions, are less likely to close.

It is however necessary to consider that the name of a museum might be associated with a museum's survival not only via its perception by other parties, but also via reflection of the founder's intentions regarding the institutions longevity; this possibility is discussed in more detail in the results section.
\paragraph*{Competition}

@@

In particular, Cox proportional hazard models allows to identify the risk that a number of variables pose for a museum's chance of closing. 
The dependent variable is an indicator of museum closure, which takes the value of 1 for the museums which close in the year of their closure, and 0 otherwise.
Typically for survival data, museums that do not close during the observation period are right-censored, i.e. for such museums the dependent variable is zero for all years as their closing has not been observed.
The Cox-proportional hazard model has the form \(h(t,\mathbf{x}) = h_0(t) \psi\), where \(\psi = \exp(\sum_{j} \mathbf{x}_j \beta_j)\); with \(h(t)\) as the hazard rate, \(h_0(t)\) as the baseline hazard rate, \(\mathbf{x}\) as the set of variables indexed by \(j\), and \(\beta\) as the coefficient vector.
Partial maximum likelihood estimation allows calculating \(\beta\) without defining the baseline hazard rate, which therefore is not constrained to a parametric form \parencite{Moore_2015_survival}.
\subsubsection*{Main Predictors}

@@

A measure of founder death is constructed as a time-varying covariate, which takes the value of 1 from the year of the founder's death onwards.
\paragraph*{Founder reputaton}

Founder reputation is measured via inclusion of the founder in the Artnews top 200 collector ranking \parencite{Artnews_ranking}.
This ranking, established in 1990, lists each year the 200 collectors the editors of the magazine consider most relevant.
For each year, a museums can have one of three values: "Not included"; in which case the founder is not included in the year in question and has not been so in the past, "Included"; when the founder is included, or "Dropped", for cases where the founder was included at some point in the past but is no longer included in the current year.
Cases where multiple individuals are involved in the founding of a private museum are resolved by aggregating the Artnews ranking inclusion history to the founder level (i.e., if only one of two founders is dropped from the Artnews ranking but the other remains included, the founder couple as a whole is considered included).
The variable is lagged by one year to avoid reverse causality, i.e. to exclude the possibility that an association is observed which is present due to founders being dropped from the ranking as a consequence of the closure of their museum.
\paragraph*{Museum Identity}

@@

Self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent, see table \ref{tbl:t_selfid}).
Since the name is one of the first aspects that stakeholders perceive when engaging with an organization, it might shape expectations and influence forms of engagement.
In particular, it might be that museums that also refer to themselves as museums are seen as more favorable and worthy of visits, collaborations and support than other museums, leading to higher survival prospects.

To ensure that inclusion of the word "museum" corresponds to the naming convention of the museum population, the names of the "Museums of the World" (MOW) database \parencite{deGruyter_2021_MOW}, a database containing over 55,000 museums, are analyzed.
In this database, 71\% of museum names contain the term "museum" (or its equivalent in other languages), which indicates a substantial convention by founders to include the term museum in the name of their institution.\footnote{While it would also be possible to construct inclusion in the MOW as an indicator of legitimacy, as it represents recognition of the organization as a museum by experts \parencite{Zuckerman_1999_illegitimacy}, preliminary investigations of the database indicated that it has been  updated only sparsely in recent years; thereby inclusion in it (or the lack therefore) does not constitute an accurate measurement of the extent of an institutions' recognition as a museum.}
At the same time, for an association between name and survival to be attributed to the name, the name and other organizational characteristics cannot be linked too closely.
This seems to be the case for museums, where membership is not subject to strong regulations: 
The term "museum" is not a protected term in the US \parencite[p.205]{Moore_2022_best} or European countries such as Germany \parencite[p.4]{Museumsbund_ICOMDE_2006_standards}, Denmark, Austria, Croatia or Finland \parencite{EGMUS_2024_reports}\footnote{While I was not able to find concrete information on the naming regulations of museums for every country, I did not find any country where such naming regulation is present.}.
Neither is membership in national or international museum associations necessary for an institution to be recognized as a museum: 
ICOM has around 3,000 institutional members \parencite{ICOM_2020_report19}, a relatively small fraction of the over 104,000 museums estimated to exist globally \parencite{UNESCO_2021_covid}, and while national associations fare somewhat better, with e.g. the American Association of Museums representing over 4,000 of the country's 35,000 museums \parencite{LOC_2019_AAM}, and the German Museumsbund representing over 1,300 \parencite{Museumsbund_2024_mitgliedmuseen} of Germany's 7,120 museums \parencite{IMF_2024_museumsstatistik}, the ability of these associations to impose standards is still limited.
In such an unregulated field, names do not clearly reflect institutional characteristics, which leaves evaluation of a musem to less institutionalized practical classification systems \parencite{van_Venrooij_2018_fuzziness}.
\paragraph*{Competition}

On a national level, density of private museum is calculated as the number of private museums per million population.
To measure competition on a local level, I first determine the coordinates of museum using the Google Maps API; the coordindates of museums which are not found that way (particularly those located in countries with limited Google presence such as South Korea, China and Russia) are searched manually (often using other map services such as Kakao Maps, Baidu Maps and Yandex Maps).
For closed museums, which often are not included in the current map databases, coordinates are also determined via addresses mentioned on snapshots in the Wayback Machine.
I then use the Global Human Settlement Layer \parencite{EC_2023_GHSL} to estimate the number of private museums and population counts inside a radius of ten kilometers around each private museum for each year.
To be able to estimate both competition and population effects separately, I do not calculate densities as per capita rates, but include the local museum counts, local population in millions as well as an interaction between the two (alternative specifications are presented in the supplementary materials).
While this operationalization is limited to private museum in the neighborhood, rather than the more complete set of all museums private museums may compete with, it is by no means a rarity to find private museums within a 10 km radius, as in 41\% museum-years one or more private museums in the surroundings are observed. 
\subsubsection*{Control variables}

@@

On the level of museum, I control for whether a museum includes the name of the founder (e.g. "Liam's Gallery" includes the name of the founder).
As another property of the name, it might be indicative of the commitment founder, but it might also might support by third parties less attractive.

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Oct  4 15:36:13 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 294 & 0.584 & 0.604 & 0.49 & 0 & 1 \\ 
   & Gender - Female & 79 & 0.157 & 0.166 & 0.37 & 0 & 1 \\ 
   & Gender - Couple & 130 & 0.258 & 0.231 & 0.42 & 0 & 1 \\ 
   & Founder died &  &  & 0.097 & 0.30 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 190 & 0.378 & 0.408 & 0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 104 & 0.207 & 0.189 & 0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 69 & 0.137 & 0.130 & 0.34 & 0 & 1 \\ 
   & Self-Identification - Other & 140 & 0.278 & 0.274 & 0.45 & 0 & 1 \\ 
   & Founder name in Museum name & 240 & 0.477 & 0.477 & 0.50 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  & 0.802 & 0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  & 0.144 & 0.35 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  & 0.053 & 0.23 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  & 0.450 & 1.26 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  & 1.337 & 1.68 & 0.000087 & 10.81 \\ 
   & Nbr PM within 10km &  &  & 1.778 & 3.14 & 0 & 16 \\ 
   & Great Recession (2008/09) &  &  & 0.076 & 0.27 & 0 & 1 \\ 
   & Covid Pandemic (2020/21) &  &  & 0.145 & 0.35 & 0 & 1 \\ 
   & Region - Africa & 8 & 0.016 & 0.012 & 0.11 & 0 & 1 \\ 
   & Region - Asia & 142 & 0.282 & 0.292 & 0.45 & 0 & 1 \\ 
   & Region - Europe & 248 & 0.493 & 0.497 & 0.50 & 0 & 1 \\ 
   & Region - Latin America & 23 & 0.046 & 0.042 & 0.20 & 0 & 1 \\ 
   & Region - North America & 72 & 0.143 & 0.138 & 0.34 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.020 & 0.019 & 0.13 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

Before discussing the regression models, I provide a descriptive account on private museum closure using the hazard and survival functions which describe variation the closing risk over the museum life-course.
The hazard rate is a non-parametric function which describes the probability of exiting at age \(t_i\) conditional on being alive, in the context of museum-years as units of analysis it can be formulated as \(h(t_i) = \frac{d_i}{n_i}\), with \(n_i\) as the number of units at risk at age \(t_i\) and \(d_i\) as the number of exits at age \(t_i\).
The survival function is the product of these conditional probabilities (\(S(t) = \prod_{t_i \geq t} \left(1-h(t_i) \right)\)) and describes the chance of surviving up to age \(t_i\).

@@

Calculating such survival statistics allows (to a degree) to assess whether private museums differ in their longevity from comparable institutions.
So far only a small number of studies has investigated museum closing rates, and these have focused on the United States, likely primarily due to data availability reasons: 
Larger non-profits in the US have to file the IRS form 990 (or its variants) to maintain their tax-deductible status, and form 990 data is publicly available \parencite{Lecy_2023_core}.
This data has been used in many studies of non-profit populations, and constitutes an effective comparison group for private museums as both share the same organizational form (non-profit) and unprofitable cultural sector environment.
So far three studies have used this data to investigate museum closure by calculating hazard rates not as a function of age but of calendar year:
\begin{itemize}
\item \textcite{Bowen_etal_1994_charitable} investigate the closing of 501(c)(3) museums in the 1981-1991 time period and, based on 271 (9.8\%) closures of a population of 2755, calculate average annual exit rates as 1.1\% (p.103).
\item \textcite{Gordon_etal_2013_insolvency} observe 35 closures based on 5,167 museum-years between 2000 and 2003 (p.368), resulting in an average annual closing rate of 0.68\% (p.377)\footnote{The difference to \cite{Bowen_etal_1994_charitable} is likely due to exclusion of organizations with revenues below 150,000 USD.}.
\item \textcite{Hager_2001_vulnerability} has conducted the only study specifically on art museums (NTEE code A51); he observes 42 closures over a period of four years (1994-1997) from a starting populaton of 448 (p.383), corresponding to an average yearly closing rate of 2.4\%, or around 1.9\% under the more realistic assumption of effectively using a five-year time period.
\end{itemize}

@@

The death of the founder is not associated with a significant difference (p=0.52) in private museum closure, i.e. museums are not significantly more likely to close after their founder has died, which provides little support to H1a.
While the point estimate is positive (0.280, corresponding to a 32\% increase in mortality for museums whose founders have died compared to those who have not), the low risk overall means that even decade-long survival prospects do not differ substantially despite the cumulative character of risk (figure \ref{fig:p_surv_death}).
